Global patterns of forest autotrophic carbon fluxes

### 2020-01-31 manuscript/manuscript draft.Rmd
text update related to geographic.area
relates to issue #49

Within the ForC database, sites within 25km^2^ of each other are clustered into geographic areas. To account for correlations in measurements between tightly clustered sites, a random effect was specified as plot nested within geographic area. *Data from the temperate regions was heavily skewed towards studies from the old-growth forests of the Pacific Northwest.*  These forests have very high FACF, and so to ensure that results were not unduly influenced by geographic sampling bias, we tried a version of the model where data were weighted according to forested land area within each Koeppen climate zone. Results were similar between the weighted and unweighted model. Because the weighted model may be prone to problems of over-fitting, we present only results of the unweighted model. {**Becky, I'd probably just delete this whole paragraph. Since we ended up not using the weighted model, it's just extra info for readers to digest.}

>>>>

Within the ForC database, geographically proximate sites are clustered into geographic areas, with proximity defined using a hierarchical cluster analysis on the distance matrix of the sites and a cutoff of 25km. To account for correlations in measurements between tightly clustered sites, a random effect was specified as plot nested within geographic area.
